---
title: "Application to real real data:pet insuraance rates in France"
output:
  html_document:
    df_print: paged
---

```{r}
library(kableExtra)
library(ggplot2)
library(dplyr)
library(tidyr)
library(rstudioapi)
library(IsoPriceR)
library(readr)
library(xtable)
# setwd(dirname(getActiveDocumentContext()$path))
getwd()

pet_insurance_FR <- read_csv("../data/pet_insurance_FR.csv")

data <- data.frame(carrier = pet_insurance_FR$Company, race = pet_insurance_FR$Race, r = as.numeric(sub("%", "", pet_insurance_FR$rate))/100, d = pet_insurance_FR$deductible, l = pet_insurance_FR$limit, x = pet_insurance_FR$Premium)
nrow(data)

```
# Descriptive statistics
## Coverage rate, deductible and limit
```{r}
(b_plot_r <- ggplot(data = data) + geom_bar(mapping = aes(x = r)) + ggplot2::labs(x= "Coverage Rate", y = "Frequency") +
    ggplot2::theme_classic(base_size = 20))
ggsave("../figures/b_plot_r.pdf", b_plot_r)
(b_plot_d <- ggplot(data = data) + geom_bar(mapping = aes(x = d)) + ggplot2::labs(x= "Deductible", y = "Frequency") +
    ggplot2::theme_classic(base_size = 20))
ggsave("../figures/b_plot_d.pdf", b_plot_d)
(b_plot_l <- ggplot(data = data) + geom_bar(mapping = aes(x = l)) + ggplot2::labs(x= "Limit", y = "Frequency") +
    ggplot2::theme_classic(base_size = 20))
ggsave("../figures/b_plot_l.pdf", b_plot_l)
```
## Premium in terms of coverage rate, and limit when deductible = 0
```{r}
(scat_plot_cp_r_l <- ggplot(data = data %>%filter(d==0)) + 
   geom_point(mapping = aes(x= l, y = x, size = r)) + 
   labs(x= "Limit", size = "Coverage Rate", title = "", y = "Commercial premium") + 
   ggplot2::theme_classic(base_size = 20) + theme(legend.position="bottom", legend.box = "vertical") + scale_size_continuous(breaks = c(0.5, 0.75, 1)) )
ggsave("../figures/scat_plot_cp_r_l.pdf", scat_plot_cp_r_l)
```

# Premium specification

```{r}
p_p <- pure_premium("xs", c("r", "d", "l"))
```

# Loss Models 

```{r}
lnorm_dist <- model("lognormal", c("mu", "sigma"))
gamma_dist <- model("gamma", c("alpha", "beta"))
pois_dist <- model("poisson", c("lambda"))
bin_dist <- model("binomial", c("a", "p"))
nbin_dist <- model("negative binomial", c("b", "p"))

loss_models <- list(
  loss_model(pois_dist, lnorm_dist, "Pois(lambda)-Lognormal(mu,sigma=1)"),
  loss_model(bin_dist, lnorm_dist, "Binomial(a=12,p)-Lognormal(mu,sigma=1)"),
  loss_model(nbin_dist, lnorm_dist, "Negative Binomial(b=1,p)-Lognormal(mu,sigma=1)"),
  loss_model(pois_dist, gamma_dist, "Pois(lambda)-Gamma(alpha,beta=1)"),
  loss_model(bin_dist, gamma_dist, "Binomial(a=12,p)-Gamma(alpha,beta=1)"),
  loss_model(nbin_dist, gamma_dist, "Negative Binomial(b=1,p)-Gamma(alpha,beta=1)"),
  loss_model(pois_dist, lnorm_dist, "Pois(lambda)-Lognormal(mu=0,sigma)"),
  loss_model(bin_dist, lnorm_dist, "Binomial(a=12,p)-Lognormal(mu=0,sigma)"),
  loss_model(nbin_dist, lnorm_dist, "Negative-Binomial(b=1,p)-Lognormal(mu=0,sigma)"),
  loss_model(pois_dist, gamma_dist, "Pois(lambda)-Gamma(alpha=1,beta)"),
  loss_model(bin_dist, gamma_dist, "Binomial(a=12,p)-Gamma(alpha=1,beta)"),
  loss_model(nbin_dist, gamma_dist, "Negative-Binomial(b=1,p)-Gamma(alpha=1,beta)")
             )
```

# Prior assumptions

```{r}
prior_mu <- prior_dist("uniform", "mu",c(-10, 10))
prior_mu_c <- prior_dist("constant", "mu",c(0))
prior_sigma <- prior_dist("uniform", "sigma", c(0,5))
prior_sigma_c <- prior_dist("constant", "sigma", c(1))

prior_alpha <- prior_dist("uniform", "alpha",c(0, 10000))
# prior_alpha_c <- prior_dist("constant", "alpha",c(1))
# prior_beta <- prior_dist("uniform", "beta", c(0, 1000000))
prior_beta_c <- prior_dist("constant", "beta", c(1))

prior_lambda <- prior_dist("uniform", "lambda", c(0, 10))
prior_a <- prior_dist("constant", "a", c(12))
prior_b <- prior_dist("constant", "b", c(1))
prior_p <- prior_dist("uniform", "p", c(0,1))


prior_distributions <- list(
  independent_priors(list(prior_lambda, prior_mu, prior_sigma_c)),
  independent_priors(list(prior_a, prior_p, prior_mu, prior_sigma_c)),
  independent_priors(list(prior_b, prior_p, prior_mu, prior_sigma_c)),
  independent_priors(list(prior_lambda, prior_alpha, prior_beta_c)),
  independent_priors(list(prior_a, prior_p, prior_alpha, prior_beta_c)),
  independent_priors(list(prior_b, prior_p, prior_alpha, prior_beta_c)),
  independent_priors(list(prior_lambda, prior_mu_c, prior_sigma)),
  independent_priors(list(prior_a, prior_p, prior_mu_c, prior_sigma)),
  independent_priors(list(prior_b, prior_p, prior_mu_c, prior_sigma))
)
length(prior_distributions)
```



```{r}
# data <- data %>% filter(race == "australian sheperd")
popSize <- 1000;  MC_R<- 2000; acc <- 1; sp_bounds <- c(0.4, 0.7); n_models <- length(prior_distributions); set.seed(1234)
#  Unparallel
# system.time(res_abc_list <- lapply(1:n_models, function(k) abc(data, prior_distributions[[k]], loss_models[[k]], p_p, popSize, MC_R, acc, sp_bounds)))
# save(res_abc_list, file = "../data/res_abc_real_data.RData")
# Going Paralell

```


# Posterior analysis

## Posterior distribution of the model parameters
```{r}
load("../data/res_abc_real_data.RData")
k <- 1

for(k in 1:n_models){
  last_cloud <- extract_last_cloud(res_abc_list[[k]])
  posterior_plots(last_cloud, prior_distributions[[k]], loss_models[[k]], ref_line = FALSE, font_size = 20 )
  # best_cloud <- extract_best_cloud(res_abc_list[[k]])
  # posterior_plots(best_cloud, prior_distributions[[k]], loss_models[[k]], ref_line = FALSE, font_size = 20 )
  ggsave(paste0("../figures/post_plot_",loss_models[[k]]$model_name, ".pdf"))
  
}

tab <- data.frame( model = sapply(1:n_models, function(k) loss_models[[k]]$model_name),
            eps = sapply(1:n_models, function(k) max(res_abc_list[[k]]$ds[[length(res_abc_list[[k]]$ds)]]))
            )
print(xtable(tab[order(tab$eps) ,]), include.rownames=FALSE)

# posterior_plots(best_cloud, prior_distributions[[k]], loss_models[[k]], ref_line = FALSE, font_size = 20 )
```

## Point estimate of key quantities

```{r}
posterior_point_estimates <- data.frame()
for(k in 1:length(res_abc_list)){
  # bp <- t(as.matrix(extract_best_particle(res_abc_list[[k]])))
  mode <- t(as.matrix(extract_mode(res_abc_list[[k]], loss_models[[k]], prior_distributions[[k]])))
  map <- t(as.matrix(colMeans(extract_last_cloud(res_abc_list[[k]]))))
  df <- rbind(compute_metric_particle(data, p_p, loss_models[[k]], map, method = "map")$estimates,
      compute_metric_particle(data, p_p, loss_models[[k]], mode, method = "mode")$estimates
      )
  posterior_point_estimates <- rbind(posterior_point_estimates, df)
}
```
### MAP and mode for each model

```{r}
tab <- posterior_point_estimates %>% filter(parm_names == "mu"| parm_names == "alpha"| parm_names == "sigma" | parm_names == "lambda"| parm_names == "p")%>% pivot_wider(names_from = c(method), values_from = parm_values)
print(xtable(tab), include.rownames=FALSE)
```


### Claim frequency and severity

```{r}
tab <- posterior_point_estimates %>% filter(parm_names == "Claim_Frequency" | parm_names == "Prob_0" | parm_names == "Claim_Amount") %>% pivot_wider(names_from = c(method,parm_names), values_from = parm_values) %>% select("model", "map_Prob_0", "mode_Prob_0", "map_Claim_Frequency", "mode_Claim_Frequency", "map_Claim_Amount", "mode_Claim_Amount")
print(xtable(tab), include.rownames=FALSE)
```

### Total Claim amount 

```{r}
tab <- posterior_point_estimates %>% filter(parm_names == "Total_Claim_Amount" | parm_names == "LR") %>% pivot_wider(names_from = c(method,parm_names), values_from = parm_values) %>% select("model", "map_LR", "mode_LR", "map_Total_Claim_Amount", "mode_Total_Claim_Amount")
print(xtable(tab), include.rownames=FALSE)
```



## Posterior predictive distribution

```{r}

posterior_predictive_distribution <- data.frame()
for(k in 1:length(res_abc_list)){
  last_cloud <- extract_last_cloud(res_abc_list[[k]])
  posterior_estimates <- compute_metric_cloud(data, p_p, loss_models[[k]], last_cloud)$estimates  
  posterior_predictive_distribution <- rbind(posterior_predictive_distribution, posterior_estimates)  
}
unique(posterior_predictive_distribution$model)

```

```{r}
library(latex2exp)
TeX(r'($Bin(a=12,p)-Gam(\alpha,\beta=1)$)')
quantity <- colnames(posterior_predictive_distribution)[2:6][1]
quantity_titles <- c("Claim Frequency", "Claim Amount", "P(N=0)", "Total Claim Amount","Loss Ratio" )
x_ticks <- c(TeX(r'($Bin(a=12,p)-Gam(\alpha,\beta=1)$)'), 
             TeX(r'($Bin(a=12,p)-LNorm(\mu,\sigma=1)$)'),
             TeX(r'($Bin(a=12,p)-LNorm(\mu=0,\sigma)$)'), 
             TeX(r'($Geom(p)-Gam(\alpha,\beta=1)$)'),
             TeX(r'($Geom(p)-LNorm(\mu,\sigma=1)$)'),
             TeX(r'($Geom(p)-LNorm(\mu=0,\sigma)$)'),
             TeX(r'($Pois(\lambda)-Gam(\alpha,\beta=1)$)'),
             TeX(r'($Pois(\lambda)-LNorm(\mu,\sigma=1)$)'),
             TeX(r'($Pois(\lambda)-LNorm(\mu=0,\sigma)$)'))
i <- 1
for(quantity in colnames(posterior_predictive_distribution)[2:6]){
  (post_boxplot <- ggplot(data = posterior_predictive_distribution) + 
     geom_boxplot(mapping = aes(x = eval(parse(text=quantity)) , y = as.factor(model))) + 
     theme_classic(base_size = 20)+ labs(x= "",  title = quantity_titles[i], y = "") +  
     scale_y_discrete(labels= x_ticks) +
     theme(axis.text.x = element_text(size = 16)))
  i <- i+1
  ggsave(paste0("../figures/post_boxplot_real_data_",quantity, ".pdf"), post_boxplot)
}
```

### f a posteriori

```{r}
iso_df <- data.frame()
k <- 1

for(k in 1:length(res_abc_list)){
  map <- t(as.matrix(colMeans(extract_last_cloud(res_abc_list[[k]]))))
  pp <- compute_metric_particle(data, p_p, loss_models[[k]], map, method = "map")$pp
  # mode <- t(as.matrix(extract_mode(res_abc_list[[k]], loss_models[[k]], prior_distributions[[k]])))
  # pp <- compute_metric_particle(data, p_p, loss_models[[k]], mode, method = "mode")$pp
  res_iso <- isoreg(pp, data$x)
  iso_df <- rbind(iso_df,
                data.frame(model = rep(loss_models[[k]]$model_name, nrow(data)), x= sort(res_iso$x), y = res_iso$yf))
}

(iso_plot <- ggplot(data = iso_df) + geom_step(mapping = aes(x= x, y = y, color = model)) +  ggplot2::theme_classic(base_size = 14) + labs(x= "Pure premium", y = "Commercial premium", title = "", color = "Model") + theme(legend.position="none")) 

ggsave("../figures/iso_real_data_all_models.pdf", iso_plot)
```

## Focus on the Poisson-Lognormal(mu=0, sigma)

```{r}
loss_model_names <- sapply(1:9, function(k) loss_models[[k]]$model_name)
k <- 1
posterior_predictive_distribution %>% filter(model == loss_model_names[k])
res_abc_pois_lnorm_sigma1 <- res_abc_list[[k]]
last_cloud <- extract_last_cloud(res_abc_list[[k]])
map <- t(as.matrix(colMeans(last_cloud)))
pp_pois_lnorm_sigma1 <- compute_metric_particle(data, p_p, loss_models[[k]], map)$pp 
data["pp"] <- pp_pois_lnorm_sigma1
res_iso <- isoreg(pp_pois_lnorm_sigma1, data$x)
iso_df <-data.frame(model = rep(loss_models[[k]]$model_name, nrow(data)), x= sort(res_iso$x), y = res_iso$yf)

(ggplot() + geom_point(data = data, mapping = aes(x = pp, y = x, color = as.factor(carrier))) + geom_step(data = iso_df, mapping = aes(x = x, y = y)) + labs(x= "Pure Premium", y = "Commercial premium", title = "", color = "") + ggplot2::theme_classic(base_size = 20) + theme(legend.position = "none")) 
ggsave("../figures/iso_pois_lnorm_sigma1.pdf")
```


