---
title: "Suplementary material: Generalized method of moments and identifiability"
output: html_notebook
---


```{r}
knitr::opts_chunk$set(echo = TRUE)
library(latex2exp)
library(IsoPriceR)
library(ggplot2)
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
getwd()
```
Let $X$ be a random variable that represents the total health related over a given time period, say one year, associated to a pet. Our goal is to find the parameter $\theta$ that best explains our market data made of insurance quotes
$$
\pi_i = f_i\left[\mathbb{E}(g_i(X))\right],\text{ }i = 1,\ldots, n,
$$
where $g_i$ are the coverage functions and $f_i$ are the loading function. The coverage functions are known and of the form
$$
g(x) = \min(\max(r\cdot x - d, 0), l),
$$
where $r$ is the rate of coverage, $d$ is the deductible and $l$ is the limit.The loading functions are unknown and will be approximated by a generic function $f$. In the first section we consider the problem of finding $\theta$ if $f_i(x)=x$ for all $i$ which is equivalent to having access to the pure premiums 

$$
p_i = \left[\mathbb{E}(g_i(X))\right],\text{ }i = 1,\ldots, n,
$$
which is not a realistic situation in practice. We then consider an isotonic regression model to approximate $f$ and compares it to a parametric curve, linear withe $f(x) = a + b\cdot x$ for simplicity. We consider an example where

$$
X = \sum_{k=1}^NU_k,
$$
where $N\sim\text{Pois}(\lambda = 3)$ and the $U_k$ are iid and lognormally distributed $U\sim\text{LogNormal}(\mu =0 , \sigma = 1)$

```{r}
set.seed(142)

# Loss model
freq_dist <- model("poisson", c("lambda"))
sev_dist <- model("lognormal", c("mu", "sigma"))
l_m <- loss_model(freq_dist, sev_dist, "Poisson-Lognormal")

# True parameter
lambda_true <- 3; mu_true <- 0; sigma_true <- 1
true_parms <- t(as.matrix(c(lambda_true, mu_true, sigma_true)))
colnames(true_parms) <- l_m$parm_names

# Data
## Sample of claim data to calculate the true pure premium via Monte Carlo
X_true <- sample_X(l_m, true_parms, R = 10000)
summary(X_true)
```


# I - Generalized method of moments

If the pure premiums 

$$
p_i = \mathbb{E}_(g_i(X)),\text{ }i = 1,\ldots, n,
$$

are available then our estimation problem becomes find $\theta$ that minimizes 

$$
d\left[p_{1:n},p_{1:n}^\theta\right] = \sum_i w_i^{RMSE}(p_i -p_i^\theta)^2,
$$

where $p_i^\theta = \mathbb{E}_{\theta}(g_i(X))$. Identifiability holds if there exists a unique $\theta^*$ such that 

$$
\theta^* = \underset{\theta\in \Theta}{\text{argmin}}\, d\left[p_{1:n},p_{1:n}^\theta\right].
$$

This condition ressembles the global identification conditions of the Generalized Method of Moments which is typically hard to show. Existence of minimum requires that $\theta\mapsto d\left[p_{1:n},p_{1:n}^\theta\right]$ is continuous and that $\Theta$ is compact. Uniqueness would then hold if $\theta\mapsto d\left[p_{1:n},p_{1:n}^\theta\right]$ is strictly convex. This condition is difficult to verify because an analytical expression of $\theta\mapsto d\left[p_{1:n},p_{1:n}^\theta\right]$ is out of our reach and this for almost all the compound sum $X$. A necessary condition is that the dimension of $\theta$ is lower than $n$ which is the number of moments we hold. Let us consider the case $n = 3$ with

$$
g_1 = 0.85\cdot X\text{, } g_2 = \max(X - 1.8, 0) \text{, and }g_3 = \min(X, 6)
$$

it is equivalent to the coverages $(r_1 = 0.85, d_1 = 0, l_1 = \infty)$, $(r_1 = 1, d_1 = 1.8, l_1 = \infty)$, and $(r_1 = 1, d_1 = 0, l_1 = 6)$. 

```{r}
## Characteristics of the pure premium which depends on the parameter of the insurance coverage
p_p <- pure_premium("xs", c("r", "d", "l"))
## Random premium parameters
n <- 3; r <- c(0.75, 1, 1); d <- c(0, 1.8, 0); l <- c(Inf, Inf, 6)

## Data frame with the insurance coverage parameters and the pure premium
th_premium <- matrix(c(r, d, l), nrow = n)
pps <- compute_pure_premia(X_true, coverage_type = "xs", th_premium)
df_pp <- data.frame(r = r, d = d, l = l, pp=pps)
df_pp
```
The pure premium computed above corresponds to a well specified case where there exists $\theta^* = \theta_0$ for which 

$$
d\left[p_{1:n},p_{1:n}^{\theta^{\ast}}\right] = 0
$$
We can check the uniqueness empirically, first in one dimension

```{r}
data <- df_pp[,c("r", "d", "l")]
data["x"] <- df_pp$pp
ths_premium <- as.matrix(data[p_p$parm_names])
lambda_true <- 3; mu_true <- 0; sigma_true <- 1

# Sigma --------------
# Pure premium calculation for a range of risk model parameters
sigmas <- seq(0.1, 2, 0.1)
cloud <- as.matrix(expand.grid(c(3), c(0),sigmas))
colnames(cloud) <- l_m$parm_names
X <- sample_X(l_m , cloud, R = 10000)
pp_fake <- compute_pure_premia(X, coverage_type = "xs", ths_premium)
                                                                     
# Calculation of the RMSE between true and wrong pure premium
ds <- sapply(1:nrow(cloud), function(k) mean((pp_fake[, k] - data$x)^2)^(1/2)) 
df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)
ggplot(data = df_ds) + geom_line(mapping = aes(x = sigma, y = ds))

# Lambda --------------
lambdas <- seq(0.1, 5, 0.1)
cloud <- as.matrix(expand.grid(lambdas, c(0),c(1)))
colnames(cloud) <- l_m$parm_names
X <- sample_X(l_m , cloud, R = 10000)
pp_fake <- compute_pure_premia(X, coverage_type = "xs", ths_premium)
                                                                     
# Calculation of the RMSE between true and wrong pure premium
ds <- sapply(1:nrow(cloud), function(k) mean((pp_fake[, k] - data$x)^2)^(1/2)) 
df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)
ggplot(data = df_ds) + geom_line(mapping = aes(x = lambda, y = ds))

# mu --------------
mus <- seq(-3, 3, 0.1)
cloud <- as.matrix(expand.grid(c(3), mus,c(1)))
colnames(cloud) <- l_m$parm_names
X <- sample_X(l_m , cloud, R = 10000)
pp_fake <- compute_pure_premia(X, coverage_type = "xs", ths_premium)
                                                                     
# Calculation of the RMSE between true and wrong pure premium
ds <- sapply(1:nrow(cloud), function(k) mean((pp_fake[, k] - data$x)^2)^(1/2)) 
df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)
ggplot(data = df_ds) + geom_line(mapping = aes(x = mu, y = ds))
```

Even if the model is misspecified it looks like we get a unique minimu in each dimension

```{r}
data <- df_pp[,c("r", "d", "l")]
data["x"] <- df_pp$pp
ths_premium <- as.matrix(data[p_p$parm_names])
lambda_true <- 3; mu_true <- 0; sigma_true <- 1

# Sigma --------------
# Pure premium calculation for a range of risk model parameters
sigmas <- seq(0.1, 2.5, 0.1)
cloud <- as.matrix(expand.grid(c(1), c(-1),sigmas))
colnames(cloud) <- l_m$parm_names
X <- sample_X(l_m , cloud, R = 10000)
pp_fake <- compute_pure_premia(X, coverage_type = "xs", ths_premium)
                                                                     
# Calculation of the RMSE between true and wrong pure premium
ds <- sapply(1:nrow(cloud), function(k) mean((pp_fake[, k] - data$x)^2)^(1/2)) 
df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)
ggplot(data = df_ds) + geom_line(mapping = aes(x = sigma, y = ds))
# 
# Lambda --------------
lambdas <- seq(0.1, 5, 0.1)
cloud <- as.matrix(expand.grid(lambdas, c(0.5),c(0.5)))
colnames(cloud) <- l_m$parm_names
X <- sample_X(l_m , cloud, R = 10000)
pp_fake <- compute_pure_premia(X, coverage_type = "xs", ths_premium)

# Calculation of the RMSE between true and wrong pure premium
ds <- sapply(1:nrow(cloud), function(k) mean((pp_fake[, k] - data$x)^2)^(1/2))
df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)
ggplot(data = df_ds) + geom_line(mapping = aes(x = lambda, y = ds))

# mu --------------
mus <- seq(-3, 3, 0.1)
cloud <- as.matrix(expand.grid(c(2), mus,c(1.5)))
colnames(cloud) <- l_m$parm_names
X <- sample_X(l_m , cloud, R = 10000)
pp_fake <- compute_pure_premia(X, coverage_type = "xs", ths_premium)

# Calculation of the RMSE between true and wrong pure premium
ds <- sapply(1:nrow(cloud), function(k) mean((pp_fake[, k] - data$x)^2)^(1/2))
df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)
ggplot(data = df_ds) + geom_line(mapping = aes(x = mu, y = ds))
```
In two dimensions

```{r}
data <- df_pp[,c("r", "d", "l")]
data["x"] <- df_pp$pp
ths_premium <- as.matrix(data[p_p$parm_names])
lambda_true <- 3; mu_true <- 0; sigma_true <- 1

# lambda and sigma----
# Pure premium calculation for a range of risk model parameters
lambdas<- seq(0.6, 5, 0.2); sigmas <- seq(0.2, 2, 0.2)
cloud <- as.matrix(expand.grid(lambdas, c(0),sigmas))
colnames(cloud) <- l_m$parm_names
X <- sample_X(l_m , cloud, R = 5000)
pp_fake <- compute_pure_premia(X, coverage_type = "xs", ths_premium)
                                                                     
# Calculation of the RMSE between true and wrong pure premium
ds <- sapply(1:nrow(cloud), function(k) mean((pp_fake[, k] - data$x)^2)^(1/2)) 
df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)
print(df_ds[df_ds$ds == min(df_ds$ds),])

# Generate custom contour levels
min_ds <- min(df_ds$ds); max_ds <- max(df_ds$ds)
breaks <- seq(min_ds, 1.5, length.out = 10)  # 5 levels from min_ds to 10
breaks <- round(c(breaks, seq(1.5, max(df_ds$ds), length.out = 2)) *100) / 100  # 10 levels from 10 to max_ds

(pp_contour_plot <- ggplot(df_ds, aes(x = lambda, y = sigma, z = ds)) + 
  geom_contour_filled(breaks = breaks) + 
  labs(x = TeX("$\\lambda$"), y = TeX("$\\sigma$"), fill = "RMSE") + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right"))

# lambda and mu----
# Pure premium calculation for a range of risk model parameters
lambdas<- seq(0.4, 5, 0.2); mus <- seq(-3, 3, 0.2)
cloud <- as.matrix(expand.grid(lambdas, mus,c(1)))
colnames(cloud) <- l_m$parm_names
X <- sample_X(l_m , cloud, R = 5000)
pp_fake <- compute_pure_premia(X, coverage_type = "xs", ths_premium)
                                                                     
# Calculation of the RMSE between true and wrong pure premium
ds <- sapply(1:nrow(cloud), function(k) mean((pp_fake[, k] - data$x)^2)^(1/2)) 
df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)
print(df_ds[df_ds$ds == min(df_ds$ds),])

# Generate custom contour levels
min_ds <- min(df_ds$ds); max_ds <- max(df_ds$ds)
breaks <- seq(min_ds, 1.5, length.out = 10)  # 5 levels from min_ds to 10
breaks <- round(c(breaks, seq(1.5, max(df_ds$ds), length.out = 2)) *100) / 100  # 10 levels from 10 to max_ds

(pp_contour_plot <- ggplot(df_ds, aes(x = lambda, y = mu, z = ds)) + 
  geom_contour_filled(breaks = breaks) + 
  labs(x = TeX("$\\lambda$"), y = TeX("$\\mu$"), fill = "RMSE") + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right"))

# mu and sigma----
# Pure premium calculation for a range of risk model parameters
sigmas<- seq(0.2, 3, 0.2); mus <- seq(-3, 3, 0.2)
cloud <- as.matrix(expand.grid(c(3), mus,sigmas))
colnames(cloud) <- l_m$parm_names
X <- sample_X(l_m , cloud, R = 5000)
pp_fake <- compute_pure_premia(X, coverage_type = "xs", ths_premium)
                                                                     
# Calculation of the RMSE between true and wrong pure premium
ds <- sapply(1:nrow(cloud), function(k) mean((pp_fake[, k] - data$x)^2)^(1/2)) 
df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)
print(df_ds[df_ds$ds == min(df_ds$ds),])

# Generate custom contour levels
min_ds <- min(df_ds$ds); max_ds <- max(df_ds$ds)
breaks <- seq(min_ds, 1.5, length.out = 10)  # 5 levels from min_ds to 10
breaks <- round(c(breaks, seq(1.5, max(df_ds$ds), length.out = 2)) *100) / 100  # 10 levels from 10 to max_ds

(pp_contour_plot <- ggplot(df_ds, aes(x = mu, y = sigma, z = ds)) + 
  geom_contour_filled(breaks = breaks) + 
  labs(x = TeX("$\\lambda$"), y = TeX("$\\sigma$"), fill = "RMSE") + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right"))
```

In 3D

```{r}
# Pure premium calculation for a range of risk model parameters
sigmas<- seq(0.4, 2, 0.2); mus <- seq(-1, 1, 0.2); lambdas <- seq(2, 4, 0.2)
cloud <- as.matrix(expand.grid(lambdas, mus,sigmas))
colnames(cloud) <- l_m$parm_names
X <- sample_X(l_m , cloud, R = 5000)
pp_fake <- compute_pure_premia(X, coverage_type = "xs", ths_premium)
                                                                     
# Calculation of the RMSE between true and wrong pure premium
ds <- sapply(1:nrow(cloud), function(k) mean((pp_fake[, k] - data$x)^2)^(1/2)) 
df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)
print(df_ds[df_ds$ds == min(df_ds$ds),])

```

```{r}
print(df_ds[df_ds$ds == min(df_ds$ds),])
ggplot(data = df_ds) + geom_line(mapping = aes(x = 1: nrow(df_ds), y = ds, color = as.factor(mu)))
nrow(df_ds)
```

```{r}
# Prior settings for the parameters
prior_lambda <- prior_dist("uniform", "lambda",c(0, 10))
prior_mu <- prior_dist("uniform", "mu",c(-3,3))
prior_sigma <- prior_dist("uniform", "sigma", c(0, 5))
prior_distributions <- list(prior_lambda, prior_mu, prior_sigma)
model_prior <- independent_priors(prior_distributions)

# Settings for the abc algorithm
popSize <- 500;  MC_R<- 500; acc <- 0.005; sp_bounds <- c(1, 1)
data <- df_pp[,c("r", "d", "l")]
data["x"] <- df_pp$pp
res_abc <- abc(data, model_prior, l_m, p_p, popSize, MC_R, acc, sp_bounds)
```
```{r}
# We retrieve the cloud of particles associated to each generation
cloud_dfs <- lapply(res_abc$Clouds, as.data.frame)
cloud_df <- do.call(rbind, cloud_dfs)
cloud_df$generation <- sort(rep(1:length(res_abc$Clouds), popSize))
cloud_df_plot <- rbind(
  data.frame(parm = cloud_df$lambda, parm_name = "lambda", generation = cloud_df$generation),
  data.frame(parm = cloud_df$sigma, parm_name = "sigma", generation = cloud_df$generation)
)
cloud_df_plot$parm_name <-as.factor(cloud_df_plot$parm_name) 
levels(cloud_df_plot$parm_name) <- c(lambda = TeX("$\\lambda$"), sigma = TeX("$\\sigma$"))
ggplot2::ggplot(data = cloud_df ) + ggplot2::geom_density(data = cloud_df, mapping = aes(x=lambda, color = as.factor(generation))) + ggplot2::labs(x=TeX("$\\lambda$"), y = "Density", color = "Generation") + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right") + ggplot2::geom_vline(ggplot2::aes(xintercept=true_parms[,1]), color="black",
                                   linetype="dashed")

ggplot2::ggplot(data = cloud_df ) + ggplot2::geom_density(data = cloud_df, mapping = aes(x=mu, color = as.factor(generation))) + ggplot2::labs(x=TeX("$\\mu$"), y = "Density", color = "Generation") + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right") + ggplot2::geom_vline(ggplot2::aes(xintercept=true_parms[,2]), color="black",
                                   linetype="dashed")

ggplot2::ggplot(data = cloud_df ) + ggplot2::geom_density(data = cloud_df, mapping = aes(x=sigma, color = as.factor(generation))) + ggplot2::labs(x=TeX("$\\sigma$"), y = "Density", color = "Generation") + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right") + ggplot2::geom_vline(ggplot2::aes(xintercept=true_parms[,3]), color="black",
                                   linetype="dashed")
```
```{r}
cloud_dfs[[length(res_abc$ds)]][res_abc$ds[[length(res_abc$ds)]] == min(res_abc$ds[[length(res_abc$ds)]]),]
```
# II - Identifiability despise the loading function. 

We do not have access to the pure premium, instead we have the commercial premiums
$$
\pi_i = f_i\left[\mathbb{E}(g_i(X))\right],\text{ }i = 1,\ldots, n,
$$

where the loading functions must be approximated. We therefore have to choose a model $f$ such that 

$$
\pi_i = f(p_{i}^\theta),\text{ }i = 1,\ldots, n  
$$
and hope that there exists a unique $\theta^*$ such that 

$$
\theta^* = \underset{\theta\in \Theta}{\text{argmin}}\, d\left[\pi_{1:n},f(p_{1:n}^\theta)\right].
$$
This typically depends on the choice for $f$ we consider isotonic and linear.

```{r}

```


```{r}

```


## Figure 2

```{r}
# Random safety loading
eta <- runif(n, 1.5, 3)

#Calculation of the commercial premium
df_pp["cp_linear"] <- eta * df_pp$pp
data <- df_pp[c("r", "d", "l")]
data["x"] <- df_pp$cp

# Scatter plot of comercial premium as a function of the pure premium
(cp_plot <- ggplot(data = df_pp) + geom_point(mapping = aes(x= pp, y = cp_linear))  + labs(x= "Pure premium", y = "Commercial premium", title = "") + ggplot2::theme_classic(base_size = 20) )
ggsave("../figures/cp_plot.pdf", cp_plot)
```
# Section 3
## Figure 3

```{r}
# Isotonic fit of commercial premium explained by pure premium
res_iso <- isoreg(df_pp$pp, df_pp$cp_linear)
df_pp <- df_pp[order(df_pp$pp), ]
df_pp["cp_iso_linear"] <- res_iso$yf

# Visualization of the isotonic fit
(iso_plot <- ggplot(data = df_pp) + geom_point(mapping = aes(x= pp, y = cp_linear)) + geom_step(mapping = aes(x= pp, y = cp_iso_linear)) +  ggplot2::theme_classic(base_size = 20) + labs(x= "Pure premium", y = "Commercial premium", title = "")) 
ggsave("../figures/iso_plot.pdf", iso_plot)
```
## Figure 4

```{r}
data <- df_pp[,c("r", "d", "l")]
data["x"] <- df_pp$pp
ths_premium <- as.matrix(data[p_p$parm_names])
lambda_true <- 3; mu_true <- 0; sigma_true <- 1

# Pure premium calculation for a range of risk model parameters
lambdas<- seq(0.5, 5, 0.1); sigmas <- seq(0.1, 2, 0.1)
cloud <- as.matrix(expand.grid(lambdas, c(0),sigmas))
colnames(cloud) <- l_m$parm_names
X <- sample_X(l_m , cloud, R = 10000)
pp_fake <- compute_pure_premia(X, coverage_type = "xs", ths_premium)
                                                                     
# Calculation of the RMSE between true and wrong pure premium
ds <- sapply(1:nrow(cloud), function(k) mean((pp_fake[, k] - data$x)^2)^(1/2)) 
df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)

# Generate custom contour levels
min_ds <- min(df_ds$ds); max_ds <- max(df_ds$ds)
breaks <- seq(min_ds, 1.5, length.out = 10)  # 5 levels from min_ds to 10
breaks <- round(c(breaks, seq(1.5, max(df_ds$ds), length.out = 2)) *100) / 100  # 10 levels from 10 to max_ds

(pp_contour_plot <- ggplot(df_ds, aes(x = lambda, y = sigma, z = ds)) + 
  geom_contour_filled(breaks = breaks) + 
  labs(x = TeX("$\\lambda$"), y = TeX("$\\sigma$"), fill = "RMSE") + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right"))
ggsave(paste0("../figures/pp_contour_plot.pdf"), pp_contour_plot)
```
## Figure 5 a)

```{r}
data["x"] <- df_pp$cp_linear
cps <- data$x

# Isotonic fit of the commercial premium associated to the wrong pure preium
ress_iso <- lapply(1:ncol(pp_fake), function(k) isoreg(pp_fake[, k], cps))
fs <- lapply(ress_iso, function(res_iso) stepfun(sort(res_iso$x), c(min(res_iso$yf) /2 ,
                                                                      res_iso$yf), f = 1))
ds <- sapply(1:nrow(cloud), function(k) mean((fs[[k]](pp_fake[, k]) - data$x)^2)^(1/2)) 

df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)
min_ds <- min(df_ds$ds)

# Generate custom contour levels
breaks <- seq(min_ds, 1, length.out = 10)  # 5 levels from min_ds to 10
breaks <- round(c(breaks, seq(1, max(df_ds$ds), length.out = 2)) *100) / 100  # 10 levels from 10 to max_ds

(cp_contour_plot_wo_rg <- ggplot(df_ds, aes(x = lambda, y = sigma, z = ds)) + 
  geom_contour_filled(breaks = breaks) +
  labs(x = TeX("$\\lambda$"), y = TeX("$\\sigma$"), fill = TeX("$\\epsilon$")) + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right"))
ggsave(paste0("../figures/cp_contour_plot_wo_rg.pdf"), cp_contour_plot_wo_rg)

```

## Figure 5 b)

```{r}
# Adding the regukarization terms
sp_bounds <- c(min(df_pp$pp / df_pp$cp_linear), max(df_pp$pp / df_pp$cp_linear))  
ds1 <- sapply(1:ncol(pp_fake), function(k) sqrt(mean((pmax(cps - pp_fake[,k] /sp_bounds[1], 0) )^2)))
ds2 <- sapply(1:ncol(pp_fake), function(k) sqrt(mean((pmax( pp_fake[,k] / sp_bounds[2] - cps , 0) )^2)))
ds <- ds + ds1 + ds2
df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)

# Generate custom contour levels
breaks <- seq(min_ds, 3.5, length.out = 10)  # 5 levels from min_ds to 10
breaks <- round(c(breaks, seq(3.5, max(df_ds$ds), length.out = 2)) *100) / 100  # 10 levels from 10 to max_ds

(cp_contour_plot_w_rg <- ggplot(df_ds, aes(x = lambda, y = sigma, z = ds)) + 
  geom_contour_filled(breaks = breaks) +
  labs(x = TeX("$\\lambda$"), y = TeX("$\\sigma$"), fill = TeX("$\\epsilon$")) + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right"))
ggsave(paste0("../figures/cp_contour_plot_w_rg.pdf"), cp_contour_plot_w_rg)
```

# Figure 6

```{r}

# Prior settings for the parameters
prior_lambda <- prior_dist("uniform", "lambda",c(0, 10))
prior_mu <- prior_dist("constant", "mu",c(0))
prior_sigma <- prior_dist("uniform", "sigma", c(0, 5))
prior_distributions <- list(prior_lambda, prior_mu, prior_sigma)
model_prior <- independent_priors(prior_distributions)

# Settings for the abc algorithm
popSize <- 1000;  MC_R<- 1000; acc <- 0.1; sp_bounds <- c(0.3, 0.66)
data <- df_pp[,c("r", "d", "l")]
data["x"] <- df_pp$cp_linear
res_abc <- abc(data, model_prior, l_m, p_p, popSize, MC_R, acc, sp_bounds)
```
```{r}
# We retrieve the cloud of particles associated to each generation
cloud_dfs <- lapply(res_abc$Clouds, as.data.frame)
cloud_df <- do.call(rbind, cloud_dfs)
cloud_df$generation <- sort(rep(1:length(res_abc$Clouds), popSize))
cloud_df_plot <- rbind(
  data.frame(parm = cloud_df$lambda, parm_name = "lambda", generation = cloud_df$generation),
  data.frame(parm = cloud_df$sigma, parm_name = "sigma", generation = cloud_df$generation)
)
cloud_df_plot$parm_name <-as.factor(cloud_df_plot$parm_name) 
levels(cloud_df_plot$parm_name) <- c(lambda = TeX("$\\lambda$"), sigma = TeX("$\\sigma$"))
```

### Figure 6 a)

```{r}
abc_gen_post_lambda <- ggplot2::ggplot(data = cloud_df ) + ggplot2::geom_density(data = cloud_df, mapping = aes(x=lambda, color = as.factor(generation))) + ggplot2::labs(x=TeX("$\\lambda$"), y = "Density", color = "Generation") + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right") + ggplot2::geom_vline(ggplot2::aes(xintercept=true_parms[,1]), color="black",
                                   linetype="dashed")
ggsave(paste0("../figures/abc_gen_post_lambda.pdf"), abc_gen_post_lambda)
```

### Figure 6 b)

```{r}
abc_gen_post_sigma <- ggplot2::ggplot(data = cloud_df ) + ggplot2::geom_density(data = cloud_df, mapping = aes(x=sigma, color = as.factor(generation))) + ggplot2::labs(x=TeX("$\\sigma$"), y = "Density", color = "Generation") + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right") + ggplot2::geom_vline(ggplot2::aes(xintercept=true_parms[,3]), color="black",
                                   linetype="dashed")
ggsave(paste0("../figures/abc_gen_post_sigma.pdf"), abc_gen_post_sigma)
```

# Appendix A

## Figure 14

```{r}
# Commercial premium linked to pure premium via a Gompertz growth curve
a <- runif(n, 5, 10) ; b <- runif(n, 2, 6) ; c <- 2
df_pp["cp_gompertz"] <- a * exp(-b*exp(-c * df_pp$pp))

# Isotonic fit of the gompertz growth curve
data <- df_pp[c("r", "d", "l")]
data["x"] <- df_pp$cp
res_iso <- isoreg(df_pp$pp, df_pp$cp_gompertz)
df_pp <- df_pp[order(df_pp$pp), ]
df_pp["cp_iso_gompertz"] <- res_iso$yf

(iso_plot <- ggplot(data = df_pp) + geom_point(mapping = aes(x= pp, y = cp_gompertz)) + geom_step(mapping = aes(x= pp, y = cp_iso_gompertz)) +  ggplot2::theme_classic(base_size = 20) + labs(x= "Pure premium", y = "Commercial premium", title = "")) 
ggsave("../figures/gompertz_iso_plot.pdf", iso_plot)

```


## Figure 15

```{r}
# Linear regression in the linear link case
res_lm_linear <- lm(df_pp$cp_linear ~ df_pp$pp)

# Linear regression in the Gompertz link case
res_lm_gompertz <- lm(df_pp$cp_gompertz ~ df_pp$pp)

# Calculation of the residuak of the linear and isotonic model
residual_df <- rbind(
  data.frame(
  residuals = res_lm_linear$residuals, 
  model = "Linear",
  link = "Linear"),
  data.frame(
  residuals = res_lm_gompertz$residuals, 
  model = "Linear",
  link = "Gompertz"),
  data.frame(
  residuals = df_pp$cp_linear - df_pp$cp_iso_linear, 
  model = "Isotonic",
  link = "Linear"), 
  data.frame(
  residuals = df_pp$cp_gompertz - df_pp$cp_iso_gompertz, 
  model = "Isotonic",
  link = "Gompertz")
  )
  
  
(residual_boxplot <- ggplot(data = residual_df) + geom_boxplot(mapping = aes(y = residuals, x = as.factor(link), color = model)) + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right") + ggplot2::labs(x= "Link function", color = "Regression model", y = "Residuals"))

ggsave(paste0("../figures/residual_boxplot.pdf"), residual_boxplot)
```







```{r}

set.seed(142)

# Loss model
freq_dist <- model("poisson", c("lambda"))
sev_dist <- model("lognormal", c("mu", "sigma"))
l_m <- loss_model(freq_dist, sev_dist, "Poisson-Lognormal")

# True parameter
lambda_true <- 3; mu_true <- 0; sigma_true <- 1
true_parms <- t(as.matrix(c(lambda_true, mu_true, sigma_true)))
colnames(true_parms) <- l_m$parm_names

# Data
## Sample of claim data to calculate the true pure premium via Monte Carlo
X_true <- sample_X(l_m, true_parms, R = 10000)

## Characteristics of the pure premium which depends on the parameter of the insurance coverage
p_p <- pure_premium("xs", c("r", "d", "l"))
## Random premium parameters
n <- 100; d <- runif(n, min = 0, max =  6); r <- runif(n, min = 0.5, max =  1); l <- rep(Inf, n)

## Data frame with the insurance coverage parameters and the pure premium
th_premium <- matrix(c(r, d, l), nrow = n)
pps <- compute_pure_premia(X_true, coverage_type = "xs", th_premium)
df_pp <- data.frame(r = r, d = d, l = l, pp=pps)

## Scatter plot of pure premium as a function of the deductibe and depending on the rate of coverage
(pp_plot <- ggplot(data = df_pp) + geom_point(mapping = aes(x= d, y = pp, size = r)) + labs(x= "d", y = "Pure premium", title = "") + ggplot2::theme_classic(base_size = 20) )
ggsave("../figures/pp_plot.pdf", pp_plot)
```
## Figure 2

```{r}
# Random safety loading
eta <- runif(n, 1.5, 3)

#Calculation of the commercial premium
df_pp["cp_linear"] <- eta * df_pp$pp
data <- df_pp[c("r", "d", "l")]
data["x"] <- df_pp$cp

# Scatter plot of comercial premium as a function of the pure premium
(cp_plot <- ggplot(data = df_pp) + geom_point(mapping = aes(x= pp, y = cp_linear))  + labs(x= "Pure premium", y = "Commercial premium", title = "") + ggplot2::theme_classic(base_size = 20) )
ggsave("../figures/cp_plot.pdf", cp_plot)
```
# Section 3
## Figure 3

```{r}
# Isotonic fit of commercial premium explained by pure premium
res_iso <- isoreg(df_pp$pp, df_pp$cp_linear)
df_pp <- df_pp[order(df_pp$pp), ]
df_pp["cp_iso_linear"] <- res_iso$yf

# Visualization of the isotonic fit
(iso_plot <- ggplot(data = df_pp) + geom_point(mapping = aes(x= pp, y = cp_linear)) + geom_step(mapping = aes(x= pp, y = cp_iso_linear)) +  ggplot2::theme_classic(base_size = 20) + labs(x= "Pure premium", y = "Commercial premium", title = "")) 
ggsave("../figures/iso_plot.pdf", iso_plot)
```
## Figure 4

```{r}
data <- df_pp[,c("r", "d", "l")]
data["x"] <- df_pp$pp
ths_premium <- as.matrix(data[p_p$parm_names])
lambda_true <- 3; mu_true <- 0; sigma_true <- 1

# Pure premium calculation for a range of risk model parameters
lambdas<- seq(0.5, 5, 0.1); sigmas <- seq(0.1, 2, 0.1)
cloud <- as.matrix(expand.grid(lambdas, c(0),sigmas))
colnames(cloud) <- l_m$parm_names
X <- sample_X(l_m , cloud, R = 10000)
pp_fake <- compute_pure_premia(X, coverage_type = "xs", ths_premium)
                                                                     
# Calculation of the RMSE between true and wrong pure premium
ds <- sapply(1:nrow(cloud), function(k) mean((pp_fake[, k] - data$x)^2)^(1/2)) 
df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)

# Generate custom contour levels
min_ds <- min(df_ds$ds); max_ds <- max(df_ds$ds)
breaks <- seq(min_ds, 1.5, length.out = 10)  # 5 levels from min_ds to 10
breaks <- round(c(breaks, seq(1.5, max(df_ds$ds), length.out = 2)) *100) / 100  # 10 levels from 10 to max_ds

(pp_contour_plot <- ggplot(df_ds, aes(x = lambda, y = sigma, z = ds)) + 
  geom_contour_filled(breaks = breaks) + 
  labs(x = TeX("$\\lambda$"), y = TeX("$\\sigma$"), fill = "RMSE") + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right"))
ggsave(paste0("../figures/pp_contour_plot.pdf"), pp_contour_plot)
```
## Figure 5 a)

```{r}
data["x"] <- df_pp$cp_linear
cps <- data$x

# Isotonic fit of the commercial premium associated to the wrong pure preium
ress_iso <- lapply(1:ncol(pp_fake), function(k) isoreg(pp_fake[, k], cps))
fs <- lapply(ress_iso, function(res_iso) stepfun(sort(res_iso$x), c(min(res_iso$yf) /2 ,
                                                                      res_iso$yf), f = 1))
ds <- sapply(1:nrow(cloud), function(k) mean((fs[[k]](pp_fake[, k]) - data$x)^2)^(1/2)) 

df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)
min_ds <- min(df_ds$ds)

# Generate custom contour levels
breaks <- seq(min_ds, 1, length.out = 10)  # 5 levels from min_ds to 10
breaks <- round(c(breaks, seq(1, max(df_ds$ds), length.out = 2)) *100) / 100  # 10 levels from 10 to max_ds

(cp_contour_plot_wo_rg <- ggplot(df_ds, aes(x = lambda, y = sigma, z = ds)) + 
  geom_contour_filled(breaks = breaks) +
  labs(x = TeX("$\\lambda$"), y = TeX("$\\sigma$"), fill = TeX("$\\epsilon$")) + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right"))
ggsave(paste0("../figures/cp_contour_plot_wo_rg.pdf"), cp_contour_plot_wo_rg)

```

## Figure 5 b)

```{r}
# Adding the regukarization terms
sp_bounds <- c(min(df_pp$pp / df_pp$cp_linear), max(df_pp$pp / df_pp$cp_linear))  
ds1 <- sapply(1:ncol(pp_fake), function(k) sqrt(mean((pmax(cps - pp_fake[,k] /sp_bounds[1], 0) )^2)))
ds2 <- sapply(1:ncol(pp_fake), function(k) sqrt(mean((pmax( pp_fake[,k] / sp_bounds[2] - cps , 0) )^2)))
ds <- ds + ds1 + ds2
df_ds <- data.frame(cloud)
df_ds <- cbind(df_ds, ds)

# Generate custom contour levels
breaks <- seq(min_ds, 3.5, length.out = 10)  # 5 levels from min_ds to 10
breaks <- round(c(breaks, seq(3.5, max(df_ds$ds), length.out = 2)) *100) / 100  # 10 levels from 10 to max_ds

(cp_contour_plot_w_rg <- ggplot(df_ds, aes(x = lambda, y = sigma, z = ds)) + 
  geom_contour_filled(breaks = breaks) +
  labs(x = TeX("$\\lambda$"), y = TeX("$\\sigma$"), fill = TeX("$\\epsilon$")) + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right"))
ggsave(paste0("../figures/cp_contour_plot_w_rg.pdf"), cp_contour_plot_w_rg)
```

# Figure 6

```{r}

# Prior settings for the parameters
prior_lambda <- prior_dist("uniform", "lambda",c(0, 10))
prior_mu <- prior_dist("constant", "mu",c(0))
prior_sigma <- prior_dist("uniform", "sigma", c(0, 5))
prior_distributions <- list(prior_lambda, prior_mu, prior_sigma)
model_prior <- independent_priors(prior_distributions)

# Settings for the abc algorithm
popSize <- 1000;  MC_R<- 1000; acc <- 0.1; sp_bounds <- c(0.3, 0.66)
data <- df_pp[,c("r", "d", "l")]
data["x"] <- df_pp$cp_linear
res_abc <- abc(data, model_prior, l_m, p_p, popSize, MC_R, acc, sp_bounds)
```
```{r}
# We retrieve the cloud of particles associated to each generation
cloud_dfs <- lapply(res_abc$Clouds, as.data.frame)
cloud_df <- do.call(rbind, cloud_dfs)
cloud_df$generation <- sort(rep(1:length(res_abc$Clouds), popSize))
cloud_df_plot <- rbind(
  data.frame(parm = cloud_df$lambda, parm_name = "lambda", generation = cloud_df$generation),
  data.frame(parm = cloud_df$sigma, parm_name = "sigma", generation = cloud_df$generation)
)
cloud_df_plot$parm_name <-as.factor(cloud_df_plot$parm_name) 
levels(cloud_df_plot$parm_name) <- c(lambda = TeX("$\\lambda$"), sigma = TeX("$\\sigma$"))
```

### Figure 6 a)

```{r}
abc_gen_post_lambda <- ggplot2::ggplot(data = cloud_df ) + ggplot2::geom_density(data = cloud_df, mapping = aes(x=lambda, color = as.factor(generation))) + ggplot2::labs(x=TeX("$\\lambda$"), y = "Density", color = "Generation") + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right") + ggplot2::geom_vline(ggplot2::aes(xintercept=true_parms[,1]), color="black",
                                   linetype="dashed")
ggsave(paste0("../figures/abc_gen_post_lambda.pdf"), abc_gen_post_lambda)
```

### Figure 6 b)

```{r}
abc_gen_post_sigma <- ggplot2::ggplot(data = cloud_df ) + ggplot2::geom_density(data = cloud_df, mapping = aes(x=sigma, color = as.factor(generation))) + ggplot2::labs(x=TeX("$\\sigma$"), y = "Density", color = "Generation") + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right") + ggplot2::geom_vline(ggplot2::aes(xintercept=true_parms[,3]), color="black",
                                   linetype="dashed")
ggsave(paste0("../figures/abc_gen_post_sigma.pdf"), abc_gen_post_sigma)
```

# Appendix A

## Figure 14

```{r}
# Commercial premium linked to pure premium via a Gompertz growth curve
a <- runif(n, 5, 10) ; b <- runif(n, 2, 6) ; c <- 2
df_pp["cp_gompertz"] <- a * exp(-b*exp(-c * df_pp$pp))

# Isotonic fit of the gompertz growth curve
data <- df_pp[c("r", "d", "l")]
data["x"] <- df_pp$cp
res_iso <- isoreg(df_pp$pp, df_pp$cp_gompertz)
df_pp <- df_pp[order(df_pp$pp), ]
df_pp["cp_iso_gompertz"] <- res_iso$yf

(iso_plot <- ggplot(data = df_pp) + geom_point(mapping = aes(x= pp, y = cp_gompertz)) + geom_step(mapping = aes(x= pp, y = cp_iso_gompertz)) +  ggplot2::theme_classic(base_size = 20) + labs(x= "Pure premium", y = "Commercial premium", title = "")) 
ggsave("../figures/gompertz_iso_plot.pdf", iso_plot)

```


## Figure 15

```{r}
# Linear regression in the linear link case
res_lm_linear <- lm(df_pp$cp_linear ~ df_pp$pp)

# Linear regression in the Gompertz link case
res_lm_gompertz <- lm(df_pp$cp_gompertz ~ df_pp$pp)

# Calculation of the residuak of the linear and isotonic model
residual_df <- rbind(
  data.frame(
  residuals = res_lm_linear$residuals, 
  model = "Linear",
  link = "Linear"),
  data.frame(
  residuals = res_lm_gompertz$residuals, 
  model = "Linear",
  link = "Gompertz"),
  data.frame(
  residuals = df_pp$cp_linear - df_pp$cp_iso_linear, 
  model = "Isotonic",
  link = "Linear"), 
  data.frame(
  residuals = df_pp$cp_gompertz - df_pp$cp_iso_gompertz, 
  model = "Isotonic",
  link = "Gompertz")
  )
  
  
(residual_boxplot <- ggplot(data = residual_df) + geom_boxplot(mapping = aes(y = residuals, x = as.factor(link), color = model)) + ggplot2::theme_classic(base_size = 20) + ggplot2::theme(legend.position="right") + ggplot2::labs(x= "Link function", color = "Regression model", y = "Residuals"))

ggsave(paste0("../figures/residual_boxplot.pdf"), residual_boxplot)
```

